Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-02-03 2019/NUMTA_Barkalov/SoftComputing/article.tex
fix formulas

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$. 
\begin{enumerate} 
  \item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}
  \item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
$$
\end{enumerate} 
From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{align}
	R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \nonumber \\
	& \geq  \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \nonumber \\
  & \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} \nonumber \\
	& = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M} \nonumber \\
	& \geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
\end{align}
And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
\begin{align}\label{R_glob_greater_R_loc}
	R_{glob}(i) & = \Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 \nonumber \\
	& > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
\end{align}
The statement is proved.

@@

	Let us show that if the conditions of Theorem \ref{theorem:1} are satisfied, the inequality $R_{glob}(j)>0$ will hold. According to the second condition of Theorem \ref{theorem:1} and to the condition (\ref{K_leq_L}), 
\begin{align}
	& z_j = g_{\nu}\left( y(x_j) \right) \leq g_{\nu}\left( y(\bar x) \right) + 2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{1/N}, \nonumber \\
	& \nu = \nu(x_j),
\end{align}
\begin{align}
	z_{j-1} & = g_{\nu}\left( y(x_{j-1}) \right) \nonumber \\
	& \leq g_{\nu}\left( y(\bar x) \right) + 2L_{\nu}\sqrt{N+3}(\bar x - x_{j-1})^{1/N}, \nonumber \\
	& \nu = \nu(x_{j-1}).
\end{align}

@@

	Then, the characteristic $R_{glob}(j)$ of the interval \\
$[x_{j-1}, x_j]$, $j=j(k)$ will be strictly positive, i.e. \\
$R_{glob}(j)>0$. Indeed, at $\nu=\nu(x_j)=\nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\small
\begin{align*}
	& R(j) = \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \Delta_i + \\ 
	& + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}} \\
	& = \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} + \\
	& + 4\frac{z_{\nu}^\ast-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \\
	& \geq \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right) + \\
	& + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \\
	& = \Delta_i\left(1-4\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}
\normalsize
At $\nu=\nu(x_j ) > \nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\begin{align*}
	& R(j) = 2\Delta_i - 4\frac{z_j-z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \\
	& \geq 2\Delta_i+4\frac{z_{\nu}^{\ast}-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} \\
	& = 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \\
	& \geq 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}

@@

\begin{table}[h!]
	\caption{Average number of iterations performed by the methods on “Simple” class}
	\label{tab:average_number_of_iterations_simple}
	\begin{tabular}[]{ccccc}
		\hline\noalign{\smallskip}
		                    & $N=2$                & $N=3$                    & $N=4$                  & $N=5$                   \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{316} & \multirow{2}{*}{7403}    & \multirow{2}{*}{40419} & \multirow{2}{*}{296357} \\
		$r_{\nu}^{loc}=1.4$ &                      &                          &                        &                         \\
		%\hline
		IA-DL,              & \multirow{2}{*}{350} & \multirow{2}{*}{8990(1)} & \multirow{2}{*}{41230} & \multirow{2}{*}{360497} \\
		$r_{\nu}^{loc}=2.0$ &                      &                          &                        &                         \\
		%\hline
		IA                  & 439                  & 11804(1)                 & 41973(3)               & 404660(2)               \\
		\hline\noalign{\smallskip}
	\end{tabular}
\end{table}

\begin{table}[h!]
	\caption{Average number of iterations performed by the methods on “Hard” class}
	\label{tab:average_number_of_iterations_hard}
	\begin{tabular}{ccccc}
		\hline\noalign{\smallskip}
		                    & $N=2$                & $N=3$                    & $N=4$                  & $N=5$                      \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{766} & \multirow{2}{*}{9636}    & \multirow{2}{*}{60904} & \multirow{2}{*}{763711}    \\
		$r_{\nu}^{loc}=1.4$ &                      &                          &                        &                            \\
		%\hline
		IA-DL,              & \multirow{2}{*}{830} & \multirow{2}{*}{12020}   & \multirow{2}{*}{57473} & \multirow{2}{*}{743874(1)} \\
		$r_{\nu}^{loc}=2.0$ &                      &                          &                        &                            \\
		%\hline
		IA                  & 1074                 & 20327                    & 87310(2)               & 1084990(2)                 \\
		\hline\noalign{\smallskip}
	\end{tabular}
\end{table}

>>>>

	\textbf{Proof}. Let us consider two possible cases of the values of the indices $\nu(x_{i-1})$ and $\nu(x_i)$. 
\begin{enumerate} 
  \item If $\nu(x_{i-1}) \neq \nu(x_i)$, then according to  formulae (\ref{R_2}), (\ref{R_3}) 
\begin{equation}\label{R_glob_1}
	R(i)=R_{glob}(i)=R_{loc}(i)=2\Delta_i>0. 
\end{equation}
  \item If $\nu(x_{i-1}) = \nu(x_i) = M$, then, taking into account (\ref{current_lower_bounds}), the following inequality will hold
$$
	z_i+z_{i-1}-2z_M^* = |z_i-z_{i-1}|\leq \mu_M\Delta_i .
$$
\end{enumerate} 
From here, it will follow that for any value $r_M>1$ the following inequalities will hold
\begin{align}
	R(i) & = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \nonumber \\
	& \geq  \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \geq \nonumber \\
  & \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \nonumber \\
	& = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M} \geq \nonumber \\
	& \geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0.
\end{align}
And because $r_{M}^{glob} > r_{M}^{loc} > 1$, then
\begin{align}\label{R_glob_greater_R_loc}
	R_{glob}(i) & = \Delta_i\left(1-\frac{1}{r_M^{glob}} \right)^2 > \nonumber \\
	& > \Delta_i\left(1-\frac{1}{r_M^{loc}} \right)^2 = R_{loc}(i).
\end{align}
The statement is proved.

@@

	Let us show that if the conditions of Theorem \ref{theorem:1} are satisfied, the inequality $R_{glob}(j)>0$ will hold. According to the second condition of Theorem \ref{theorem:1} and to the condition (\ref{K_leq_L}), 
\begin{align}
	& z_j = g_{\nu}\left( y(x_j) \right) \leq g_{\nu}\left( y(\bar x) \right) + 2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{1/N}, \nonumber \\
	& \nu = \nu(x_j),
\end{align}
\begin{align}
	z_{j-1} & = g_{\nu}\left( y(x_{j-1}) \right) \leq \nonumber \\
	& \leq g_{\nu}\left( y(\bar x) \right) + 2L_{\nu}\sqrt{N+3}(\bar x - x_{j-1})^{1/N}, \nonumber \\
	& \nu = \nu(x_{j-1}).
\end{align}

@@

	Then, the characteristic $R_{glob}(j)$ of the interval \break
$[x_{j-1}, x_j]$, $j=j(k)$ will be strictly positive, i.e. \break
$R_{glob}(j)>0$. Indeed, at $\nu=\nu(x_j)=\nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\small
\begin{align*}
	& R(j) = \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \Delta_i + \\ 
	& + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}}\\
	& = \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} + \\
	& + 4\frac{z_{\nu}^\ast-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right) + \\
	& + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} = \\
	& = \Delta_i\left(1-4\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}
\normalsize
At $\nu=\nu(x_j ) > \nu(x_{j-1})$ and the value $r_{\nu}=r_{\nu}^{glob}$
\begin{align*}
	& R(j) = 2\Delta_i - 4\frac{z_j-z_{\nu}^{\ast}}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i+4\frac{z_{\nu}^{\ast}-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} = \\
	& = 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq \\
	& \geq 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^{\ast}-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0.
\end{align*}

@@

\begin{table}[h!]
	\caption{Average number of iterations performed by the methods on “Simple” class}
	\label{tab:average_number_of_iterations_simple}
	\begin{tabular}[]{ccccc}
		\hline\noalign{\smallskip}
		                    & $N=2$                & $N=3$                    & $N=4$                  & $N=5$                   \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{316} & \multirow{2}{*}{7403}    & \multirow{2}{*}{40419} & \multirow{2}{*}{296357} \\
		$r_{\nu}^{loc}=1.4$ &                      &                          &                        &                         \\
		\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{350} & \multirow{2}{*}{8990(1)} & \multirow{2}{*}{41230} & \multirow{2}{*}{360497} \\
		$r_{\nu}^{loc}=2.0$ &                      &                          &                        &                         \\
		\noalign{\smallskip}
		IA                  & 439                  & 11804(1)                 & 41973(3)               & 404660(2)               \\
		\hline\noalign{\smallskip}
	\end{tabular}
\end{table}

\begin{table}[h!]
	\caption{Average number of iterations performed by the methods on “Hard” class}
	\label{tab:average_number_of_iterations_hard}
	\begin{tabular}{ccccc}
		\hline\noalign{\smallskip}
		                    & $N=2$                & $N=3$                    & $N=4$                  & $N=5$                      \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{766} & \multirow{2}{*}{9636}    & \multirow{2}{*}{60904} & \multirow{2}{*}{763711}    \\
		$r_{\nu}^{loc}=1.4$ &                      &                          &                        &                            \\
		\noalign{\smallskip}
		IA-DL,              & \multirow{2}{*}{830} & \multirow{2}{*}{12020}   & \multirow{2}{*}{57473} & \multirow{2}{*}{743874(1)} \\
		$r_{\nu}^{loc}=2.0$ &                      &                          &                        &                            \\
		\noalign{\smallskip}
		IA                  & 1074                 & 20327                    & 87310(2)               & 1084990(2)                 \\
		\hline\noalign{\smallskip}
	\end{tabular}
\end{table}
